---
title: "Introduction to obmodeling"
author: "Jeffrey Mazar and Brian G. Peterson"
date: "`r Sys.Date()`"
output: ioslides_presentation
vignette: >
  %\VignetteIndexEntry{Introduction to obmodeling}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
# setup block that doesn't show up in the output
knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(cache = TRUE)
require(obmodeling)
require(quantstrat)
require(knitr)
require(pander)
panderOptions("digits", 2)
```

## Introduction

This is an **R** package which uses *xts* time series objects to manipulate and 
analyze:

- Depth of the market at a given time

- Volume

- Price movement through the day

- Weighted Midpoint (Cartea 2015)

- Market spread (Jong 2009, 91–96)

- Measures of liquidity (Cartea 2015)

- Measures of volatility (Jong 2009, 92; Cartea 2015)

- PIT/VPIT (O. Easley D. 1996; L. de P. Easley D. 2012)

- Price pressure (Hendershot 2014; Rama Cont 2011)

- Trade imbalance (Rama Cont 2011)

## Setup

```{r testdata, echo=TRUE}

# load the data here, ob_trades & ob_quotes

load.quotes(system.file('extdata/ob_quotes.csv',package = 'obmodeling'))

```

## Visualize  Order Book

```{r, echo=TRUE, results='asis'}

chart.depth('ESH6')

```

## Pretty Pictures 2



## Pretty Pictures 3



## Thanks


#References

