---
title: "Introduction to obmodeling"
author: "Jeffrey Mazar and Brian G. Peterson"
date: "`r Sys.Date()`"
output: 
  ioslides_presentation:
    df_print: kable
bibliography: obmodeling.bib
vignette: >
  %\VignetteIndexEntry{Introduction to obmodeling}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
# setup block that doesn't show up in the output
knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(cache = TRUE)
require(obmodeling)
require(quantstrat)
require(knitr)
require(pander)
panderOptions("digits", 2)
```

## Introduction

obmodeling is an **R** package which uses *xts* time series objects to manipulate and 
analyze:

- Depth of the market at a given time

- Price movement, liquidity changes [@Cartea2015]

- Market spread [@DeJong2009, pp. 91–96]

- Measures of volatility [@DeJong2009 p. 92, and @Cartea2015]

- PIN/VPIN [@Easley1996, @Easley2012a]

- Price pressure [@Hendershott2014, @Cont2014]

- Trade imbalance [@Cont2014]

## Setup

```{r testdata, echo=TRUE}

# load the data here, ob_trades & ob_quotes

load.quotes(system.file('extdata/ob_quotes.csv',package = 'obmodeling'))
load.trades(system.file('extdata/ob_trades.csv',package = 'obmodeling'))


```

- *obmodeling* uses an environment to store parsed trades and quotes
- you can access that environment via `getOB()`

## Visualize Order Book

```{r, echo=TRUE, message=FALSE}

chart.depth('ESH6')

```

## Pretty Pictures 2



## Pretty Pictures 3



## Thanks

**Thank You for Your Attention**

find it on github at:  https://github.com/jmazar/obmodeling

install via:

`install_github('jmazar/obmodeling')`

Patches and contributions welcome!

## References {.smaller}
